Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
appendix structure

@@

\section{Variable managment}
The variables in each synchronisation vector are considered local: for
a given pNet expression, we must have fresh local variables for each
occurrence of a vector (= each time we instantiate rule
Tr2). Similarly the state variables of each copy of a given pLTS in
the system, must be distinct, and those created for each application
of Tr2 have to be fresh and all distinct. This will be implemented
within the open-automaton generation algorithm, e.g. using name
generation using a global counter as a suffix.
\TODO{add structure of generated names}

@@

\noindent
\TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}

\begin{tabular}{p{5cm}p{7cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		\multicolumn{2}{l}{Variables:}
		\\
		$\dfrac{\EEnv \vdash x:A }
                       {x \translate \texttt{(declare-const x A)}}$&
		\\\specialrule{0em}{3pt}{3pt}
		Open transition: 
		\\
		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Assign) \translate lst_1 lst_2}$
		\\\specialrule{0em}{3pt}{3pt}
		Predicate: & Predicate conjunct:
		\\
		$\dfrac{Pred = \bigwedge\limits_{k\in K}P_k}{Pred \translate \texttt{map} \translate P_k}$&	$\dfrac{P_k = op(args)}{P_k \translate \texttt{(assert (op map}\longrightarrow \texttt{args))}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{\EEnv \vdash x:A }{Var(x) \longrightarrow \texttt{x}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op') = 0}{op' \longrightarrow name(op')}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op')\neq 0}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
		\\\specialrule{0em}{3pt}{3pt}
		Assignment: 
		\\
		$\dfrac{Assign = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Ass(x_k)}{Assign \translate \texttt{map} \translate (x_k, a_k)}$
		\\\specialrule{0em}{3pt}{3pt}		
		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
		\\\\\specialrule{0em}{1pt}{1pt}
	        \hline
\end{tabular}

\paragraph{Presentation of algebra}

\TODO{Improve this, inserting the main definition from the ``Checker'' document}
%% Open pNet framework provides us
%% with a model able to express the semantics of many different algebras
%% or languages. In particular,
As seen in section
\ref{section:pnets}, the \emph{term algebra} used to express the
action expressions and data parameters is left open in
the pNet definition.

So, for a given language, we now need to specify its data and action
domains, giving them an abstract syntax (sorts, constructors, operators,
and predicates). We call this a \emph{Presentation}.
We also define a concrete syntax, that will be used for
pretty-printing, but also for translating the presentation, and the
predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
Fig~\ref{schema:smt-lib}).

An algebra presentation contains:

\begin{itemize}
	\item Sorts: Constants sets of the algebra or types of the data
          and actions (integer and boolean sort are implicitly
          declared).  There \emph{must} be one sort for actions, and
          eventually others for the types of data
          parameters. In the LOTOS example, 
          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
          r, p, q, acc \} .$

	\item Operators:
          %Operators used to construct action expressions; they are
          constructors and predicates for data and action sorts. For
          instance, in our LOTOS example, we
          have a generic action constructor ``$ACT$'', taking as
          argument an action litteral and a data parameter, declared as:
          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
        \item Constants: The satisfiability solver need to know which
          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
          $r$ of the controllers in running example). 
          For a given pNet system, the sort $Action$ will include all
          these constants.
\end{itemize}

\paragraph{Interaction with Z3}
%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
%There are several ways to interact with the Z3 solver. 
%It is possible to use Z3 interactively using the SMT-LIB
%(Python-based) language. 
From inside our algorithm code, we submit satisfiability requests to
Z3 using its JAVA API. Here for readability, we
show the Z3 code using its SMT-LIB input language. As an
example in
Fig~\ref{schema:smt-lib}, we show the input for checking the
transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
of the LOTOS action algebra types 
and constructors, then the declaration of variables, and finally the
predicate to be checked, encoded as a set of assertions.
%% Generally, some $datatypes$ are declared to input the sorts, while here
%% we only declare one $datatypes$ named $Action$ to involve all the
%% constant actions. Then we input the predicate of this open transition
%% in two parts: the variables contained in the predicate are declared
%% first, then the terms of predicate are inputed as $assertions$ one by
%% one. 
The result "unsat" in the output is just what we expected.

%\TODO{edit the figure to make it smaller in height [DONE]}

%We present the architecture of the interaction with Z3 in
%Fig~\ref{schema:interaction}.
%For each OT generated at the toplevel of a pNet, the predicate must be
%submitted for satisfiability check to Z3. For that we need to
%translate into Z3 (Java-API) syntax, both the elements of the action
%algebra, and the predicates itself, including the encoding of the
%variable assignments (the Post part).
%
%The $presentation$ of the action algebra
%is declared at the beginning of the algorithm as the $sorts$ and the
%$operators$ will be used throughout the whole algorithm. It is
%translated into $datatypes$ and $functions$ then submitted to the Z3
%at the same time. Each candidate predicate will then be translated
%into $assertions$ before submitted to Z3 after the algorithm
%computing out all the possible open transitions, they act as
%intermediate results there. Together with the $datatypes$ and
%$functions$, the $assertions$ are used to check the satisfiability of
%the predicate in Z3.

\paragraph{Translation of Action algebra presentation}
\TODO{Exerpt of the formalisation}
The $datatypes$ are declared according to the $sorts$ the users
declared in the $presentation$. If the return type of the $functions$
is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
So when we declare the operator ACT we illustrated in section 4.1, it
will be just declared together with the constants like :\\
\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}

The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}

%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently. The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
%
%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
%
%It will be translated into the Z3 statement: 
%
%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]

\paragraph{Translating assignments into predicate terms}
\TODO{Exerpt of the formalisation}

@@

% We check the satisfiability of open transitions on the top level of
% the pNet, treating these open transitions as the intermediate result
% of the algorithm. After we get the intermediate results of open
% transitions, we check them one by one.
Here we declare first all the variables in the predicates, with their
sorts.
An example of syntax is::\\
\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}

\noindent Then each term of the
predicate is an assertion in Z3, as an example, in the former
unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
from which we generate the following two assertions:\\
\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}

\noindent The predicate submitted to the Z3 also contains the
assignments encodings.
In the case of $ot_2$, it
gives the assertion:\\
\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}

\subsection{Simplification of Predicates}
\subsection{Simplification of Predicates}
\ERIC{: motivated, add refs, and an abstract presentation of stuff
  from pages 19-20. The following is NOT a good example, we should
  rather use a pNet with at least 2 levels, to have real intermediate
variables; here b0, b1, b2 are NOT intermediate variables... and the
predicate simplification is using `some form of ``tautology checking''
rather thanm rewritting.}

@@

%\subsubsection{Result of CCS example}
%\QIN{
%also can present all the possible behavior of that CCS formula with 16 open
%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
%In this example, there are 32 more transitions detected unsatisfiable by Z3.
%}
%
%\QIN{
%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
%}
%
%\begin{figure}[h]
%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
%  
%  $\begin{array}{@{}r@{}l@{}}
%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
%  \end{array}$
%  
%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
%\end{figure}

%% \QIN{
%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
%% the open automaton for them. 
%% }

% \newpage
%\appendix

\section{More details on the generation algorithm}

%\paragraph{Fresh variables management.}

% This will be implemented within the open-automaton generation algorithm,
% e.g. using name generation using a global counter as a suffix.

% \TODO{To be move  by Xudong}

%\subsection{Presentation of algebra}
%One of the important goal of the Open pNet framework is to provide us
%with a model able to express the semantics of many different algebras
%or languages. In particular, as we have seen in section
%\ref{section:pnets}, the \emph{term algebra} used to express the
%action expressions and the data in their parameters is left open in
%the pNet formalization.
%
%So, for a given language, we now need to specify its data and action
%domains, giving them an abstract syntax (sorts, constructors, operators,
%and predicates). We call this a \emph{Presentation}.
%We also define a concrete syntax, that will be used for
%pretty-printing, but also for translating the presentation, and the
%predicates, into Z3 syntax (we shall detail this translation in
%section \ref{section:pruning}).
%
%An algebra presentation contains:
%\begin{itemize}
%	\item Sorts: Constants sets of the algebra or types of the data
%          and actions. In every presentation, sorts for integer and
%          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
%several others for the types of data parameters. In the LOTOS example,
%we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
%
%	\item Operators: Operators used to construct action
%          expressions (including their data parameters); they are
%          constructors of data and action sorts, but also predicates
%          over these objects. For instance, in our LOTOS example, we
%          could have two constructor functions ``$DELTA$'' and ``$ACC$''
%          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
%          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
%        \item Constants: The satisfiability solver need to know which
%          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
%          $r$ of the controllers in running example). 
%          For a given pNet system, a sort $Action$ will include all
%          these constants.
%\end{itemize}

%We need introduce operators for building expressions, of both action
%and data sorts, when encoding the 
%algebra into pNets. So that is needed to know about the input and
%output of the operators used in the expressions from those
%algebra. The input and output should belong to the sorts of the
%pNet. When there are $k$ sorts in this pNet, the structure of a
%$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
%\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
%% We  introduce operators for building expressions, either action
%% expressions or predicate terms, when encoding the algebra into
%% pNets. The operators here are treated as functions, with the sorts of
%% the pNet acting as the types of their input and output. 
%% For instance, in our LOTOS running example, we use a function ``$ACT$'' action to construct the action expression $\delta(x)$ and $acc(x)$. We can define the operator as a binary operator with the format like:

%%  \[\OTvar{ACT:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]

%\paragraph{Implementation of the expression meta-model}
% \TODO{maybe we could remove this paragraph (and the figure)}
%The VerCors platform uses Ecore and EMF to define the structure of
%both pNets and actions algebras. There exists a predefined set of
%action and data expressions classes, including boolean, integer and
%action expressions, with predefined variables, literal (constants),
%and operators. Operators can be categorized into unary, binary and
%N-ary operators.
%The original version of VerCors did not allow to extend these classes,
%we have modified its architecture so that a user can extend them,
%defining more elements for his specific algebra.
%
%In Fig~\ref{schema:expression-pnets}, we show the Expression class we
%improved, including extensions for CCS and LOTOS.
%
%\begin{figure}[t]
%  \includegraphics[width=\linewidth]{XFIG/Expression}
%  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
%\end{figure}

%\TODO{give an example of user-defined sorts/operators, and tell that
%  you will give it's translation into Z3 in section 5.4}

% \TODO{To be move / replace by Xudong}

%\subsection{Computing and using open automata}
%In this section we present an algorithm to construct the open
%automaton representing the behavior of an open pNet, and show
%under which conditions this automaton is finite.
%
%\begin{alg}[behavioral semantics of open pNets: Sketch]
%This is a standard residual algorithm over a set of open-automaton
%states, but where transitions are open transitions
%constructively ``proven'' by deduction trees.
%
%1) Start with a set of unexplored states containing the initial state
%of the automaton, and an empty set of explored states.
%
%2) While there are unexplored states:
%
%2a) pick one state from the unexplored set and add it to the explored
%set. From this state
%build all possible deduction trees by application of the structural
%rules Tr1 and Tr2, using all applicable combinations
%of synchronization vectors.
%
%2b) For each deduction trees, extract the resulting
%open-transition.
%Its predicate is checked (using Z3) for  satisfiability. If it is
%unsatisfiable, the resulting OT is discarded. This will minimize the
%number of resulting transitions. 
%
%2c) For each open-transition,  add the transition in the outgoing transitions of
%the current state, and add the
%resulting state in the unexplored set if it is not already in the
%explored set.
%
%3) Finally a reachability check could potentially
%prune the state space.
%
%\end{alg}

%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}

%% To have some practical interest, it is important to know when this
%% algorithm terminates. The following theorem shows that an open-pNet
%% with finite synchronization sets, finitely many leaves and
%% holes, and each pLTS at leaves having a finite number of states and
%% (symbolic) transitions, has a finite automaton. The proof can be found
%% in \cite{henrio:Forte2016}.

%% \begin{theorem}[Finiteness of open-automata.]\\
%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
%%   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
%%   are finite, and if
%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
%% has a finite number of state variables, then Algorithm 1 terminates
%% and produces an open automaton 
%% $\mathcal{T}$ with finitely many states and transitions.

% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
%   J}$,
% build its semantics as in algorithm 1.

% We have:

% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
%   \to finite{(\mathcal{T})}$$
% \end{theorem}

\subsection{Algebra specification}
\subsection{Term algebra: type system and static semantics}
\subsection{Fresh variables}

%The variables in each synchronization vector are considered local, so
%does the variables of an open transition such as its hole behaviors
%and its result action. So we want rename the variables to make them
%unique on every occurrence of a vector. Similarly, the name given to
%the hole behaviors for each hole or the result action for each open
%transition must be distinct. At the same time, we also hope them still
%readable. Here we rename the variables with a regular format using the fresh function.

Application of the semantic rules require generating a lot of fresh
names, for different kind of variables. We could use a global name
generator to guarantee unicity, but 
at the same time, we also hope them still
readable. Here we rename the variables with a regular format using the fresh function.
More precisely, the fresh function generates a new name adding a
suffix after the original name. The suffix contains three parts
combined by a colon.

For example, in the running example, the first possible behavior of
the hole, it doesn't have a name, only have the prefix ``hb''. The
hole is the second subnets of the root node so its ``tree index'' is
``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
\subsection{Variable managment}
\subsection{Filtering the behaviour combinations}
\subsection{Translation to SMTlib input language}
\subsection{Elimination of intermediate variables}

\section{Full examples}
\TODO{May be we use two architecture examples here, a simpler one,
  before the Failure Timer ?}
\subsection{A very simple architecture}
\subsection{Full input for the FailureTimer architecture}
\subsection{Full output for the FailureTimer open automaton}

@@

>>>>

To have some practical interest, it is important to know when this
algorithm terminates. The following theorem shows that an open-pNet
with finite synchronization sets, finitely many leaves and
holes, and each pLTS at leaves having a finite number of states and
(symbolic) transitions, has a finite automaton. The proof can be found
in \cite{henrio:Forte2016}.

\begin{theorem}[Finiteness of open-automata.]\\
Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
  are finite, and if
$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
has a finite number of state variables, then Algorithm 1 terminates
and produces an open automaton 
$\mathcal{T}$ with finitely many states and transitions.

Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
    K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
  J}$,
build its semantics as in algorithm 1.

We have:

$$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
  \to finite{(\mathcal{T})}$$
\end{theorem}

@@

\section{Variable managment}
The variables in each synchronisation vector are considered local: for
a given pNet expression, we must have fresh local variables for each
occurrence of a vector (= each time we instantiate rule
Tr2). Similarly the state variables of each copy of a given pLTS in
the system, must be distinct, and those created for each application
of Tr2 have to be fresh and all distinct. This will be implemented
within the open-automaton generation algorithm, e.g. using name
generation using a global counter as a suffix.

\paragraph{Fresh variables}
Application of the semantic rules require generating a lot of fresh
names, for different kind of variables. We could use a global name
generator to guarantee unicity, but 
at the same time, we also hope them still
readable. Here we rename the variables with a regular format using the fresh function.
More precisely, the fresh function generates a new name adding a
suffix after the original name. The suffix contains three parts
combined by a colon.

For example, in the running example, the first possible behavior of
the hole, it doesn't have a name, only have the prefix ``hb''. The
hole is the second subnets of the root node so its ``tree index'' is
``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.

@@

% \TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}

\noindent
\begin{tabular}{p{5cm}p{7cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		\multicolumn{2}{l}{Variables:}
		\\
		$\dfrac{\EEnv \vdash x:A }
                       {x \translate \texttt{(declare-const x A)}}$&
		\\\specialrule{0em}{3pt}{3pt}
		Open transition: 
		\\
		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Assign) \translate lst_1 lst_2}$
		\\\specialrule{0em}{3pt}{3pt}
		Predicate: & Predicate conjunct:
		\\
		$\dfrac{Pred = \bigwedge\limits_{k\in K}P_k}{Pred \translate \texttt{map} \translate P_k}$&	$\dfrac{P_k = op(args)}{P_k \translate \texttt{(assert (op map}\longrightarrow \texttt{args))}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{\EEnv \vdash x:A }{Var(x) \longrightarrow \texttt{x}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op') = 0}{op' \longrightarrow name(op')}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op')\neq 0}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
		\\\specialrule{0em}{3pt}{3pt}
		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
		\\\specialrule{0em}{3pt}{3pt}
		Assignment: 
		\\
		$\dfrac{Assign = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Ass(x_k)}{Assign \translate \texttt{map} \translate (x_k, a_k)}$
		\\\specialrule{0em}{3pt}{3pt}		
		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
		\\\\\specialrule{0em}{1pt}{1pt}
	        \hline
\end{tabular}

\paragraph{Translating assignments into predicate terms}

@@

%% \paragraph{Checking satisfiability}

%% % We check the satisfiability of open transitions on the top level of
%% % the pNet, treating these open transitions as the intermediate result
%% % of the algorithm. After we get the intermediate results of open
%% % transitions, we check them one by one.
%% Here we declare first all the variables in the predicates, with their
%% sorts.
%% An example of syntax is::\\
%% \centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}

%% \noindent Then each term of the
%% predicate is an assertion in Z3, as an example, in the former
%% unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
%% \centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
%% from which we generate the following two assertions:\\
%% \centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}

%% \noindent The predicate submitted to the Z3 also contains the
%% assignments encodings.
%% In the case of $ot_2$, it
%% gives the assertion:\\
%% \centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}

\subsection{Simplification of Predicates}
\TODO{I keep it here for now, but I think we shall not include it in
  the FM submission, this section is not mature enough}

\ERIC{: motivated, add refs, and an abstract presentation of stuff
  from pages 19-20. The following is NOT a good example, we should
  rather use a pNet with at least 2 levels, to have real intermediate
variables; here b0, b1, b2 are NOT intermediate variables... and the
predicate simplification is using `some form of ``tautology checking''
rather than rewritting.}

@@

\section{Full examples}

\subsection{Full input for the FailureTimer architecture}
\subsection{Full output for the FailureTimer open automaton}

@@

\TODO{Not yet !}
